---
title: "Assess Food View Task block counterbalance"
author: "baf44"
date: ""
output: html_document
editor_options: 
  chunk_output_type: console
---

## Question: was randomization/counterbalancing of image blocks across toy/food conditions successful?

#### Set up

Import libraries
```{r imports, include=TRUE, echo=TRUE, results='hide', warning=FALSE, message=FALSE}
library(dplyr)
library(stringr) # for substring()
library(ggplot2)
library(purrr) # for map_chr()
```

Import events.tsv files
```{r load data, include=TRUE}
# set base directory (contains bids/)
base_dir = "/Users/baf44/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/b-childfoodlab_Shared/Active_Studies/MarketingResilienceRO1_8242020/ParticipantData/"

# get list of events files
events_files <- Sys.glob(file.path(base_dir, "bids", "rawdata",  "sub*", "ses-1", "func", "*foodview*events.tsv"))

# read events files into list of dataframes
events_data_list <- lapply(events_files, read.delim, sep = "\t", na.strings = "n/a")

# make 1 dataframe with all events data
events_data <- do.call(rbind, events_data_list)

# data1 <- lapply(events_files[1], read.delim, sep = "\t", na.strings = "n/a")[[1]]
```

Subset events data to '.jpeg' events. Only these rows are needed to determine whether image blocks were effectively counterbalanced
```{r prep jpeg_data, include=TRUE}

# subset jpeg rows
jpeg_data <- events_data[grepl(".jpeg", events_data$stim_file_name), ]

# make new column for image set based on first 4 characters of stim_file_name
jpeg_data$image_set <- substring(jpeg_data$stim_file_name, first=1, last=4)

# make new column for image block based on stim_file_name (exclude last 6 characters)
jpeg_data$image_block <- gsub('.{6}$', '', jpeg_data$stim_file_name)

```

```{r assess task completion by sub, include=TRUE}
image_counts_by_sub <- jpeg_data %>% group_by(sub) %>% summarise(n_blocks = n()) 
incomplete_subs <- as.list(image_counts_by_sub$sub[image_counts_by_sub$n_blocks < 80])

jpeg_data_completed_task <- jpeg_data[!jpeg_data$sub %in% incomplete_subs,]
```

#### Assess administration of block types by condition

Task design: Food images were grouped within blocks characterized by (1) set (A-D), (2) energy density (ED; high/low), and (3) taste (sweet/savory), leading to a total of 4*2*2 = 16 unique image_blocks (e.g., 'setA_high_savory'), divided across 4 runs. This means that across all participants, image_block 'setA_high_savory' contained the same 5 high-ED/savory food items. All blocks in a run were of the same set. The task was design so each participant saw each image_block once, after either food or toy commercial (i.e., food/toy commercial_cond). 

Set order across runs were counter balanced across the options: ADCB, BADC, CBAD, DCBA.
Within each set (A-D), the order of food and commercial conditions was (pseudorandomized?)
How was the order of image_block in a run determined?? 

Set and commerical block orders were pre-determined based on subject ID.

First, lets verify then number of unique image_blocks and that each participant saw each image_block a maximum of 1 time.
```{r count image_block by sub, include=TRUE, message=FALSE}

# count number of times an image_block was shown for each sub (1 block = 5 jpeg events)
block_counts_by_sub <- jpeg_data %>% group_by(sub, commercial_cond, image_block) %>% summarise(n_blocks = n()/5) 

# number of unique blocks
print(paste0("number of unique image_blocks: ", length(unique(block_counts_by_sub$image_block))))
print(paste0("Unique image_blocks: ", paste(unique(block_counts_by_sub$image_block), collapse = ", ")))

# confirm subjects never got the same image_block > 1x
print(paste0("number of subjects with repeated image blocks: ", sum(block_counts_by_sub$n_blocks > 1)))
```

To assess whether image_blocks were counterbalanced across condition, the following chunk will plot the number of times each image_block occurred by condition.
```{r summarize jpeg_data, include=TRUE, message=FALSE}

# get number of each image_block by commercial_cond
block_counts_by_cond <- jpeg_data %>% group_by(commercial_cond, image_block) %>% summarise(n_blocks = n()/5) 

# plot number of blocks by condition, separately for each image_block
ggplot(block_counts_by_cond,
       aes(x = commercial_cond,
           y = n_blocks, fill = commercial_cond)) + 
  geom_bar(stat = "identity",
           position = "dodge") + 
  facet_wrap(~image_block)

# plot number of blocks/person by condition, separately for each image_block -- akin to % of time the image_block/condition combination occurs across the sample
ggplot(block_counts_by_cond,
       aes(x = commercial_cond,
           y = n_blocks/length(unique(jpeg_data$sub)), fill = commercial_cond)) + 
  geom_bar(stat = "identity",
           position = "dodge") + 
  facet_wrap(~image_block)

# get number of set+ED blocks by commercial_cond
ed_block_counts_by_cond <- block_counts_by_cond %>% mutate(
  image_set = map_chr(strsplit(image_block, '_'), 1),
  image_ed = map_chr(strsplit(image_block, '_'), 2),
) %>% group_by(commercial_cond, image_set, image_ed) %>% summarise(n_blocks = sum(n_blocks)) %>% mutate(image_set_ed = str_c(image_set, image_ed, sep = "_"))

# plot number of blocks by condition, separately for each set/ED combo
ggplot(ed_block_counts_by_cond,
       aes(x = commercial_cond,
           y = n_blocks, fill = commercial_cond)) + 
  geom_bar(stat = "identity",
           position = "dodge") + 
  facet_wrap(~image_set_ed, ncol = 2)

# get number of set+taste blocks by commercial_cond
taste_block_counts_by_cond <- block_counts_by_cond %>% mutate(
  image_set = map_chr(strsplit(image_block, '_'), 1),
  image_taste = map_chr(strsplit(image_block, '_'), 3)
) %>% group_by(commercial_cond, image_set, image_taste) %>% summarise(n_blocks = sum(n_blocks)) %>% mutate(image_set_taste = str_c(image_set, image_taste, sep = "_"))

# plot number of blocks by condition, separately for each set/taste combo
ggplot(taste_block_counts_by_cond,
       aes(x = commercial_cond,
           y = n_blocks, fill = commercial_cond)) + 
  geom_bar(stat = "identity",
           position = "dodge") + 
  facet_wrap(~image_set_taste, ncol = 2)


```

