---
title: "fMRI food view task summary"
author: "baf44"
output:
  html_document: default
  pdf_document: default
editor_options:
  chunk_output_type: console
  markdown: 
    wrap: 72
---

This document provides a summary of data collection progress, fMRI quality, and task behavior for the Foodview Task including:

1.  Task completion by run

2.  Histograms of fMRI data quality metrics by run

    1.  \% trs with framewise displacement (FD) \> .9

    2.  Average FD

    3.  Signal-to-noise ratio (SNR)

3.  Histograms of of task behavior by commerical condition (food, toy)

    1.  Response rate 

    2.  Reaction time 

    3.  % items with "want" (vs. "not want") ratings



# Set up

Load packages, import data
```{r imports, warning=FALSE, message=FALSE}
library(ggplot2)
library(tidyr)
library(dplyr)

# set base_dir 
base_dir = "/Users/baf44/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/b-childfoodlab_Shared/Active_Studies/MarketingResilienceRO1_8242020/ParticipantData/"

# import data from MRIQC
mriqc_path <- file.path(base_dir, "bids", "derivatives", "mriqc", "group_bold.tsv")
mri_qc = read.delim(mriqc_path)

# import behavioral data
beh_path <- file.path(base_dir, "bids", "derivatives", "beh_summary_databases", "foodview_long_by_cond.tsv")
beh = read.delim(beh_path)

```

Prepare MRIQC output for graphing
```{r, warning=FALSE, message=FALSE}

# subset foodview runs
foodview_qc <- mri_qc[grepl("foodview", mri_qc$bids_name),]
  
# make run column
foodview_qc$run <-
  ifelse(grepl("run-01", foodview_qc$bids_name), "Run 1",
         ifelse(grepl("run-02", foodview_qc$bids_name), "Run 2",
           ifelse(grepl("run-03", foodview_qc$bids_name), "Run 3", 
              ifelse(grepl("run-04", foodview_qc$bids_name), "Run 4", NA))))

# make sub column
foodview_qc$sub <- substr(foodview_qc$bids_name, 1, 7)
```

# Data summary

## 1.  Task completion by run

```{r, warning=FALSE, message=FALSE}
# number of scans by run
xtabs(~run, data = foodview_qc)

```


## 2. Histograms of data quality metrics by run

```{r histograms, include=TRUE, warning=FALSE, message=FALSE}
# compute summary stats by run and add to foodview_qc
foodview_qc <- foodview_qc %>% group_by(run) %>%  mutate(mean_fd_perc = mean(fd_perc),
                                                         mean_fd_mean = mean(fd_mean),
                                                         mean_snr = mean(snr),
                                                         med_fd_perc = median(fd_perc),
                                                         med_fd_mean = median(fd_mean),
                                                         med_snr = median(snr)
                                                         )


stats <- c("mean"="red", "median"="blue")

ggplot(foodview_qc,aes(fd_perc))+geom_histogram(alpha=0.4, position="identity")+facet_wrap(~as.factor(run),ncol=1) +
  scale_x_continuous(breaks = round(seq(0, max(foodview_qc$fd_perc), by = 10),1)) +
  geom_vline(aes(xintercept = mean_fd_perc, group = run, color="mean")) +
  geom_vline(aes(xintercept = med_fd_perc, group = run, color="median")) +
  scale_color_manual(name = "statistic", values = c(median = "blue", mean = "red")) + 
  xlab("Percent of TRs with framewise displacement > .9 (ABCD censoring threshold)") + 
  ylab("Number of children") + 
  theme_bw() +
  theme(axis.line = element_line(color='black'),
  plot.background = element_blank(),
  panel.grid.minor = element_blank(),
  panel.grid.major = element_blank())

ggplot(foodview_qc,aes(fd_mean))+geom_histogram(alpha=0.4, position="identity")+facet_wrap(~as.factor(run),ncol=1) +
  scale_x_continuous(breaks = round(seq(0, max(foodview_qc$fd_mean), by = .5),1)) +
  geom_vline(aes(xintercept = mean_fd_mean, group = run, color="mean")) +
  geom_vline(aes(xintercept = med_fd_mean, group = run, color="median")) +
  scale_color_manual(name = "statistic", values = c(median = "blue", mean = "red")) + 
  xlab("Average framewise displacement") + 
  ylab("Number of children")+
  theme_bw() +
  theme(axis.line = element_line(color='black'),
  plot.background = element_blank(),
  panel.grid.minor = element_blank(),
  panel.grid.major = element_blank())

ggplot(foodview_qc,aes(snr))+geom_histogram(alpha=0.4, position="identity")+facet_wrap(~as.factor(run),ncol=1) +
  scale_x_continuous(breaks = round(seq(min(foodview_qc$snr), max(foodview_qc$snr), by = .2),1)) +
  geom_vline(aes(xintercept = mean_snr, group = run, color="mean")) +
  geom_vline(aes(xintercept = med_snr, group = run, color="median")) +
  scale_color_manual(name = "statistic", values = c(median = "blue", mean = "red")) + 
  xlab("Average SNR") + 
  ylab("Number of children") +
  theme_bw() +
  theme(axis.line = element_line(color='black'),
  plot.background = element_blank(),
  panel.grid.minor = element_blank(),
  panel.grid.major = element_blank())

```

## 3. Histograms of of task behavior by commerical condition

```{r, warning=FALSE, message=FALSE}

ggplot(beh, aes(x=as.numeric(p_resp)*100, fill=commerical_cond)) + 
  geom_histogram(alpha=0.4, position="identity") + theme_bw() +
  xlim(0, 100) + 
  xlab("Response rate (%), across all runs") + 
  ylab("Number of children")

ggplot(beh, aes(x=as.numeric(avg_rt), fill=commerical_cond)) + 
  geom_histogram(alpha=0.4, position="identity") + theme_bw() +
  xlab("Average Reaction Time, across all runs (ms)") + 
  ylab("Number of children")

ggplot(beh, aes(x=as.numeric(p_want_of_resp)*100, fill=commerical_cond)) + 
  geom_histogram(alpha=0.4, position="identity") + theme_bw() +
  xlim(0, 100) + 
  xlab("% of items wanted out of items responded to, across all runs") + 
  ylab("Number of children")

```
