---
title: "fMRI food view task summary"
author: "baf44"
output:
  html_document: default
  pdf_document: default
editor_options:
  chunk_output_type: console
  markdown: 
    wrap: 72
---

This document provides a summary of data collection progress, fMRI quality, and task behavior for the Foodview Task including:

1.  Task completion by run

2.  Histograms of fMRI data quality metrics by run

    1.  \% trs with framewise displacement (FD) \> .9

    2.  Average FD

    3.  Signal-to-noise ratio (SNR)

3.  Histograms of of task behavior by commerical condition (food, toy)

    1.  Response rate 

    2.  Reaction time 

    3.  % items with "want" (vs. "not want") ratings



# Set up

Load packages, import data
```{r imports, warning=FALSE, message=FALSE}
library(ggplot2)
library(tidyr)
library(dplyr)

# set base_dir 
base_dir = "/Users/baf44/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/b-childfoodlab_Shared/Active_Studies/MarketingResilienceRO1_8242020/ParticipantData/"

# import data from MRIQC
bold_qc_path <- file.path(base_dir, "bids", "derivatives", "mriqc", "group_bold.tsv")
bold_qc = read.delim(bold_qc_path)

anat_path <- file.path(base_dir, "bids", "derivatives", "mriqc", "group_T1w.tsv")
anat_qc = read.delim(anat_path)


# import behavioral data
beh_path <- file.path(base_dir, "bids", "derivatives", "beh_summary_databases", "foodview_long_by_cond.tsv")
beh_byblock_path <- file.path(base_dir, "bids", "derivatives", "beh_summary_databases", "foodview_long_by_block.tsv")

beh = read.delim(beh_path)
beh_byblock = read.delim(beh_byblock_path)

# import participants file 
participants_path <- file.path(base_dir, "bids", "participants.tsv")
participants = read.delim(participants_path, na.strings = 'n/a')


```

Prepare MRIQC output for graphing
```{r, warning=FALSE, message=FALSE}

## BOLD Data ##
# subset foodview runs
foodview_qc <- bold_qc[grepl("foodview", bold_qc$bids_name),]
  
# make run column
foodview_qc$run <-
  ifelse(grepl("run-01", foodview_qc$bids_name), "Run 1",
         ifelse(grepl("run-02", foodview_qc$bids_name), "Run 2",
           ifelse(grepl("run-03", foodview_qc$bids_name), "Run 3", 
              ifelse(grepl("run-04", foodview_qc$bids_name), "Run 4", NA))))

# make sub column
foodview_qc$sub <- substr(foodview_qc$bids_name, 1, 7)

## Anat subs ##
anat_subs <- data.frame(substr(anat_qc$bids_name, 1, 7))
colnames(anat_subs) <- c("sub")
anat_subs$run <- "anat"

```

# Data summary

## 1.  Task completion by run

```{r task completion based on mriqc output, warning=FALSE, message=FALSE}

# add anat to foodview_qc
mriqc_runs <- rbind(anat_subs, foodview_qc[c('sub','run')])

# add risk to mriqc_runs
mriqc_runs <- mriqc_runs %>% left_join(participants[c("participant_id", "risk_status_maternal")], by = join_by(sub == participant_id))


mriqc_runs_clean <- mriqc_runs[!is.na(mriqc_runs$run),]

ggplot(mriqc_runs_clean, aes(x = run)) +
  geom_bar() + theme_bw() + ylim(0, 80) +
  theme(axis.text=element_text(size=14, colour = "black"),
        plot.title = element_text(hjust = 0.5, size=18),
        axis.title = element_text(size=18))+ 
  xlab("Food View Task Run") +
  ylab("Number of scans")

# by risk status
```


```{r task completion based on beh, warning=FALSE, message=FALSE}

runs <- beh_byblock[beh_byblock$block_num == 4, c("sub", "run_num")]

# add risk to mriqc_runs
runs <- runs %>% left_join(participants[c("participant_id", "risk_status_maternal")], by = join_by(sub == participant_id))


ggplot(runs, aes(x = run_num)) +
  geom_bar() + theme_bw() + ylim(0, 80) +
  xlab("Food View Task Run") +
  ylab("Number of scans") + 
  theme(axis.text=element_text(size=24, colour = "black"), axis.title =element_text(size=24, face = "bold", colour = "black"))

# stacked: by risk 
ggplot(runs, aes(x = run_num, fill = risk_status_maternal)) +
  geom_bar() + theme_bw() + ylim(0, 80) +
  xlab("Food View Task Run") +
  ylab("Number of scans") + 
  theme(axis.text=element_text(size=20, colour = "black"), 
        axis.title =element_text(size=20, face = "bold", colour = "black"),
        legend.text = element_text(size=20),
        legend.title = element_text(size=20)) +
  scale_fill_discrete(name = "Risk Status", type=c("coral","skyblue", "grey"))


# grouped: by risk 
ggplot(runs, aes(x = run_num, fill = risk_status_maternal)) +
  geom_bar(position = "dodge") + theme_bw() + ylim(0, 40) +
  xlab("Food View Task Run") +
  ylab("Number of scans") + 
  theme(axis.text=element_text(size=24, colour = "black"), axis.title =element_text(size=24, face = "bold", colour = "black"))

```


## 2. Histograms of data quality metrics by run

Overall
```{r histograms, include=TRUE, warning=FALSE, message=FALSE}
# compute summary stats by run and add to foodview_qc
foodview_qc <- foodview_qc[!is.na(foodview_qc$run),] %>% group_by(run) %>%  mutate(mean_fd_perc = mean(fd_perc),
                                                         mean_fd_mean = mean(fd_mean),
                                                         mean_snr = mean(snr),
                                                         med_fd_perc = median(fd_perc),
                                                         med_fd_mean = median(fd_mean),
                                                         med_snr = median(snr)
                                                         )


stats <- c("mean"="red", "median"="blue")

fd_perc_plot <- ggplot(foodview_qc,aes(fd_perc))+geom_histogram(alpha=0.4, position="identity")+facet_wrap(~as.factor(run),ncol=1) +
  scale_x_continuous(breaks = round(seq(0, max(foodview_qc$fd_perc), by = 10),1)) +
  geom_vline(aes(xintercept = mean_fd_perc, group = run, color="mean")) +
  geom_vline(aes(xintercept = med_fd_perc, group = run, color="median")) +
  scale_color_manual(name = "statistic", values = c(median = "blue", mean = "red")) + 
  xlab("% of TRs with framewise displacement > .9") + 
  ylab("Number of children") + 
  theme_bw() +
  theme(axis.line = element_line(color='black'),
  plot.background = element_blank(),
  panel.grid.minor = element_blank(),
  panel.grid.major = element_blank())  +
  theme(axis.text=element_text(size=20, colour = "black"), axis.title =element_text(size=24, face = "bold", colour = "black"),
        strip.text.x = element_text(size = 24),
        legend.text = element_text(size=24),
        legend.title = element_text(size=24)
        )

fd_mean_plot <- ggplot(foodview_qc,aes(fd_mean))+geom_histogram(alpha=0.4, position="identity")+facet_wrap(~as.factor(run),ncol=1) +
  scale_x_continuous(breaks = round(seq(0, max(foodview_qc$fd_mean), by = .5),1)) +
  geom_vline(aes(xintercept = mean_fd_mean, group = run, color="mean")) +
  geom_vline(aes(xintercept = med_fd_mean, group = run, color="median")) +
  scale_color_manual(name = "statistic", values = c(median = "blue", mean = "red")) + 
  xlab("Average framewise displacement") + 
  ylab("Number of children")+
  theme_bw() +
  theme(axis.line = element_line(color='black'),
  plot.background = element_blank(),
  panel.grid.minor = element_blank(),
  panel.grid.major = element_blank())

snr_plot <- ggplot(foodview_qc,aes(snr))+geom_histogram(alpha=0.4, position="identity")+facet_wrap(~as.factor(run),ncol=1) +
  scale_x_continuous(breaks = round(seq(min(foodview_qc$snr), max(foodview_qc$snr), by = .2),1)) +
  geom_vline(aes(xintercept = mean_snr, group = run, color="mean")) +
  geom_vline(aes(xintercept = med_snr, group = run, color="median")) +
  scale_color_manual(name = "statistic", values = c(median = "blue", mean = "red")) + 
  xlab("Average SNR") + 
  ylab("Number of children") +
  theme_bw() +
  theme(axis.line = element_line(color='black'),
  plot.background = element_blank(),
  panel.grid.minor = element_blank(),
  panel.grid.major = element_blank())

fd_perc_plot
```

By risk status

```{r histograms, include=TRUE, warning=FALSE, message=FALSE}


foodview_qc_risk <-
  foodview_qc %>% 
  left_join(participants[c("participant_id", "risk_status_maternal")], by = join_by(sub == participant_id)) %>% 
  filter(!is.na(risk_status_maternal)) %>% filter(!is.na(run))

ggplot(foodview_qc_risk, aes(fd_perc)) + 
  geom_boxplot(aes(fill=risk_status_maternal))+ 
  facet_wrap(~as.factor(run),ncol=1) +
#  labs(x = "Phase", y = "Growth",color="Type" )+
  scale_fill_brewer(palette="Blues")+
  theme_bw()+
  theme(strip.background=element_rect(fill="black"),
        strip.text=element_text(color="white", face="bold"),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())
 
```

## 3. Histograms of task behavior by commerical condition 

```{r, warning=FALSE, message=FALSE}

ggplot(beh, aes(x=as.numeric(p_resp)*100, fill=commerical_cond)) + 
  geom_histogram(alpha=0.4, position="identity") + theme_bw() +
  xlim(0, 100) + 
  xlab("Response rate (%)") + 
  ylab("Number of children") +
  ylim(0, 11) +
  theme(axis.text=element_text(size=24, colour = "black"), axis.title =element_text(size=24, face = "bold", colour = "black"),
        legend.text = element_text(size=18, colour = "black"),
        legend.title = element_text(size=18, colour = "black")) +
  guides(fill=guide_legend(title="Commericial \nCondition"))

ggplot(beh, aes(x=as.numeric(avg_rt), fill=commerical_cond)) + 
  geom_histogram(alpha=0.4, position="identity") + theme_bw() +
  xlab("Average Reaction Time (ms)") + 
  ylab("Number of children") +
  ylim(0, 11) +
  theme(axis.text=element_text(size=24, colour = "black"), axis.title =element_text(size=24, face = "bold", colour = "black"),
        legend.text = element_text(size=18, colour = "black"),
        legend.title = element_text(size=18, colour = "black")) +
  guides(fill=guide_legend(title="Commericial \nCondition"))

ggplot(beh, aes(x=as.numeric(p_want_of_resp)*100, fill=commerical_cond)) + 
  geom_histogram(alpha=0.4, position="identity") + theme_bw() +
  xlim(0, 100) + 
  ylim(0, 11) +
  xlab("% 'want' responses") + 
  ylab("Number of children") +
  theme(axis.text=element_text(size=24, colour = "black"), axis.title =element_text(size=24, face = "bold", colour = "black"),
        legend.text = element_text(size=18, colour = "black"),
        legend.title = element_text(size=18, colour = "black")) +
  guides(fill=guide_legend(title="Commericial \nCondition"))


```

