---
title: "REACH Data Collection"
author: "baf44"
output:
  html_document: default
  pdf_document: default
editor_options:
  chunk_output_type: console
---

figure out how document can be viewed on github ?
https://rmarkdown.rstudio.com/github_document_format.html

```{r setup, include=FALSE}
library(devtools)
library(padr)
library(tidyverse)
library(lubridate)
library(ggplot2)
library(tidyr)
library(table1)
library(here)

load_all("/Users/baf44/projects/dataREACHr")

# set base_dir
base_dir = "/Users/baf44/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/b-childfoodlab_Shared/Active_Studies/MarketingResilienceRO1_8242020/ParticipantData/"

# define names of redcap files to process
source(here("ParticipantData", "bids", "code", "config_redcap_sourcedata.R")) # use here() to ensure consistent relative paths regardless of where the code is run from (e.g., console or R Markdown knitting).

#### process redcap data ####

# assign paths to data downloaded from redcap
visit_data_path = file.path(base_dir, "bids", "sourcedata", "phenotype", visit_file_name)
data_de_path = file.path(base_dir, "bids", "sourcedata", "phenotype", double_entry_file_name)

# process redcap data
redcap_data <-
  proc_redcap(visit_data_path,
              data_de_path,
              overwrite = FALSE,
              return_data = TRUE)

# process task data
task_data <-
  proc_task(
    base_wd = base_dir,
    overwrite_sourcedata = FALSE,
    overwrite_rawdata = FALSE,
    overwrite_jsons = FALSE,
    return_data = TRUE
  )

```

```{r format processed redcap data, include=FALSE}

#extract participants data
participants_data <- redcap_data$phenotype_data$participants

# add bmi values used in screening to participants_data
anthro_data <- redcap_data$phenotype_data$anthropometrics
participants_data <- merge(participants_data, anthro_data[anthro_data$session_id == "ses-1", c("participant_id", "child_bmi_p", "maternal_bmi")], by = "participant_id", all = TRUE)
colnames(participants_data)[colnames(participants_data) == "child_bmi_p"] <- "child_bmi_p_v1"
colnames(participants_data)[colnames(participants_data) == "maternal_bmi"] <- "maternal_bmi_v1"

# remove rows without visits
participants_data <- participants_data[!participants_data$visit_protocol_order == "",]

# make column eligibility_status based on V1 assessments of child BMI and maternal risk status
participants_data <- participants_data %>% mutate(
  eligibility_status = case_when(
    !is.na(risk_status_maternal) & child_bmi_p_v1 <= 90 ~ "elligible",
    is.na(risk_status_maternal) & child_bmi_p_v1 <= 90 ~ "bmi_not_risk",
    !is.na(risk_status_maternal) & child_bmi_p_v1 > 90 ~ "risk_not_bmi",
    TRUE ~ NA
  ),
  eligibility_status = factor(eligibility_status, levels=c("bmi_not_risk", "risk_not_bmi", "elligible"))
  )

# make long dataframe of visit dates
visits_long <- participants_data %>%
  pivot_longer(cols = child_protocol_1_date:child_protocol_5_date, names_to = "child_protocol_number", values_to = "child_protocol_date") %>%
  filter(!is.na(child_protocol_date)) %>% mutate(
    child_protocol_number = gsub("child_protocol_|_date", "", child_protocol_number)
  )

# extract redcap download date from visit_file_name
visit_download_date = strsplit(visit_file_name, split = "_")[[1]][[3]]

# make lists of low-risk and high-risk children (regardless of child BMI)
high_risk = participants_data[(participants_data$risk_status_maternal == 'high-risk' & !is.na(participants_data$risk_status_maternal)), "participant_id"]
low_risk = participants_data[(participants_data$risk_status_maternal == 'low-risk' & !is.na(participants_data$risk_status_maternal)), "participant_id"]
```

# Visit progress

This summary was generated on `r Sys.Date()` using data downloaded from Redcap on `r visit_download_date`

## Weekly visit summary

```{r weekly update, echo = FALSE}
date = Sys.Date()
week_start_date = Sys.Date() - 7

# subset data from the past week
week_visits_long <- visits_long[visits_long$child_protocol_date >= week_start_date,]

# make table of counts by risk and protocol for the past week
label(week_visits_long$child_protocol_number) <- "Child Visit Protocol" #update label for table
risk_by_visit_week_table <- table1(~ child_protocol_number | risk_status_maternal, data=week_visits_long)


```

Dates: `r week_start_date` to `r date`

**Total visits: `r nrow(week_visits_long)`**

Table 1. This week's visit count by protocol and risk status `r risk_by_visit_week_table`

```{r n visits cince last meeting, echo = FALSE}
print(paste("Number of visits since last investigators meeting (2023-12-19):", sum(visits_long$child_protocol_date > as.Date("2023-12-19"))))
```


## Overall study progress

```{r enrollement by race/ethnicity, echo = FALSE}

# add factor labels
visits_long <- visits_long %>%
  mutate(ethnicity = recode(ethnicity, `0` = "NOT Hispanic or Latino", `1` = "Hispanic or Latino"),
         race = recode(race, `0` = "American Indian/Alaskan Native", `1` = "Asian", `2` = "Black or African American", `3` = "White", `4` = "Hawaiian/Pacific Islander", `5` = "Other")
         )

# race ethnicity enrollment
# enrollment table - race and ethnicicty by sex
enrollement_table <- table1(~ race + ethnicity | sex, data=visits_long[visits_long$child_protocol_number == 1,])

# enrollement table - race by ethincity*sex -- requires no missing values (NA) for ethnicity, recode NAs as unknown/not reported
visits_long$ethnicity[is.na(visits_long$ethnicity)] <- "Unknown/Not reported"
visits_long$race[is.na(visits_long$race)] <- "Unknown/Not reported"

enrollement_table_2 <- table1(~ race | ethnicity*sex, data=visits_long[visits_long$child_protocol_number == 1,])

```

Table 2. Enrollment table `r enrollement_table_2`

```{r age distribution at enrollment, echo=FALSE}

ggplot(participants_data, aes(x=child_protocol_1_age)) + geom_histogram(binwidth=.5, color="black", fill="white", boundary = 0) +
  scale_x_continuous(breaks = seq(7,10,.5), labels = seq(7,10,.5)) + xlab("Age (years)") +
  ggtitle("Child Age Distribution at Visit 1") + 
  theme(axis.title=element_text(size=14,face="bold"),
        axis.text=element_text(size=12),
        plot.title = element_text(hjust = 0.5, size=18))
  
```


```{r time series plot, echo = FALSE}

# get start and latest dates
start_date <- min(visits_long$child_protocol_date, na.rm = TRUE)
latest_date <- max(visits_long$child_protocol_date, na.rm = TRUE)

# define function to get cumulative count of visits by date
cumulative_visit_counter <- function(data, var) {
  # data is name of dataframe
  # var is character vector of column name

  count_data <- data %>% count(.data[[var]], name = "counts") %>%
  filter(!is.na(.data[[var]])) %>% pad(
    start_val = start_date,
    end_val = latest_date,
    interval = "day"
  ) %>% fill_by_value(counts, value = 0) %>%
  mutate("{var}_cumcount" := cumsum(counts)) %>%
  select(-counts)
  
  return(count_data)
}

# Create a sequence of dates between the start and end dates
date_sequence <- data.frame(date = seq.Date(from = start_date, to = latest_date, by = "day"))

# apply cumulative_visit_counter for each child_protocol_date and add data to date_sequence
for (var in c("child_protocol_1_date", "child_protocol_2_date", "child_protocol_3_date", "child_protocol_4_date", "child_protocol_5_date") ) {

  counts <- cumulative_visit_counter(participants_data, var)

  date_sequence <- date_sequence %>%
    left_join(counts, by = c("date" = var))
}

# make cumulative_long from date_sequence
cumulative_long <- date_sequence %>% 
  pivot_longer(
    cols = c("child_protocol_1_date_cumcount", "child_protocol_2_date_cumcount", "child_protocol_3_date_cumcount", "child_protocol_4_date_cumcount", "child_protocol_5_date_cumcount"), 
    names_to = "visit",
    values_to = "count"
)

# plot cumulative count over time by visit
ggplot(cumulative_long, aes(x = date, y = count)) +
  geom_line(aes(color = visit), linewidth = 1) +
  scale_y_continuous(breaks = seq(0, 100, len = 11)) +
  ggtitle("Cumulative number of visits over time") +
  labs(color = "Child Visit Protocol") +
  scale_color_discrete(
    labels = c(
      "1",
      "2",
      "3",
      "4",
      "5"
    )
  ) +
  theme_minimal() + 
  theme(axis.title=element_text(size=14,face="bold"),
        axis.text=element_text(size=12),
        plot.title = element_text(hjust = 0.5, size=22)) + 
  geom_vline(xintercept = as.numeric(as.Date("2023-12-19")), 
             color = "black", linetype = "dashed", size = 1) +
  annotate("text", x = as.Date("2023-12-01"), y = 80, label = "Last investigators meeting", angle='90')

```

```{r barplot: visits by eligibility status, echo = FALSE}

# stacked bar chart 
ggplot(visits_long,
       aes(x = child_protocol_number, fill = eligibility_status)) +
  geom_bar() +
  scale_fill_manual(
    values = c("tomato","deepskyblue","chartreuse3"),
    labels = c(
      'Does not meet risk criteria',
      'Meets risk criteria, bmi_p > 90%',
      'Meets risk criteria, bmi_p <= 90%'
    )
  ) +
  ggtitle("Number of visits attended by elligibilty status") +
  xlab("Child Visit Protocol") +
  labs(fill = "Elligibility after V1") +
  scale_y_continuous(breaks = seq(0, 100, len = 11)) +
  theme_minimal() +
  theme(panel.grid.major.x = element_blank()) # remove the vertical grid lines


# # side by side 
# ggplot(visits_long, aes(x = child_protocol_number, y = after_stat(count), fill = eligibility_status)) +
#   geom_bar(position = "dodge", stat = "count") +
#   theme_minimal()


```


```{r table: visits by risk/sex, echo=FALSE}

visits_long_copy <- visits_long

visits_long_copy$risk_status_maternal[is.na(visits_long_copy$risk_status_maternal)] <- "neither"

visits_long_copy$child_protocol_number <- 
  factor(visits_long_copy$child_protocol_number, 
         levels=c(1,2,3,4,5),
         labels=c("Visit 1", # Reference
                  "MRI visit", 
                  "Behavioral Visit A",
                  "Behavioral Visit B",
                  "Visit 5"
                  ))
labels <- list(
    variables=list(risk_status_maternal="Maternal Risk Status",
                   sex="Child Sex"),
    groups=list("Baseline", "Follow-up"))

strata <- c(split(visits_long_copy, visits_long_copy$child_protocol_number))

footnote <- "MRI Visits occur before or after Behavioral Visits A and B depending on scanner availability"

table1(strata, labels, groupspan=c(4, 1), footnote = footnote)
```


```{r barplot: visits by risk, echo=FALSE}

# Plot: visit protocol counts by risk status
ggplot(visits_long, aes(x = child_protocol_number, y = after_stat(count), fill = risk_status_maternal)) +
  geom_bar(position = position_dodge(preserve = "single"), stat = "count") +
  labs(title = "Number of visits attended by risk status", x = "Visit protocol", y = "Count") +
  labs(fill = "Maternal risk status") +
  xlab("Child Visit Protocol") +
  scale_fill_manual(
    values = c("blue4","skyblue")) +
  theme_minimal()

```

```{r barplot: visits by sex, echo=FALSE}

# Plot: visit protocol counts by sex
ggplot(visits_long, aes(x = child_protocol_number, y = after_stat(count), fill = sex)) +
  geom_bar(position = position_dodge(preserve = "single"), stat = "count") +
  labs(title = "Number of visits attended by child sex", x = "Visit protocol", y = "Count") +
  labs(fill = "Sex") +
  xlab("Child Visit Protocol") +
  theme_minimal()

```


```{r barplot: visits by risk and sex, echo=FALSE}

# Plot: visit protocol counts by risk sex
ggplot(visits_long, aes(x = child_protocol_number, y = after_stat(count), fill = sex)) +
  geom_bar(position = position_dodge(preserve = "single"), stat = "count") +
  labs(title = "Number of visits attended by child risk and sex", x = "Visit protocol", y = "Count") +
  labs(fill = "Sex") +
  xlab("Child Visit Protocol") +
  theme_minimal() + 
  facet_wrap(~risk_status_maternal)

```

# Non-MRI Task Progress 

```{r task counts for repeated tasks, echo=FALSE  }

repeated_tasks <- c("toolbox_data", "pit_data")

# initialize list
repeated_task_counts_list <- list()

# get counts for each task and risk combo, collect info in list of dataframes
for ( task in repeated_tasks ) {

  # subset subs by condition
  subs_ses1 <- names(task_data[[task]][['ses-1']]) # list subs with ses-1 data
  subs_ses2 <- names(task_data[[task]][['ses-2']]) # list subs with ses-2 data

  subs_ses1_and2 <- intersect(subs_ses1,subs_ses2) # list subs with ses-1 and ses-2 data
  subs_ses1_not2 <- setdiff(subs_ses1, subs_ses2) # list subs with ses-1 but not ses-2
  subs_ses2_not1 <- setdiff(subs_ses2, subs_ses1) # list subs with ses-2 but not ses-1

  for (risk in c("high-risk", "low-risk")) {

    risk_subs <- participants_data[(participants_data$risk_status_maternal == risk & !is.na(participants_data$risk_status_maternal)), "participant_id"]
        
    # create dataframe of 1 row with counts for task/risk combo
    task_risk_df_row <-
      data.frame(
        task = task,
        risk = risk,
        n_ses1_and2 = length(intersect(subs_ses1_and2,risk_subs)),
        n_ses1_not2 = length(intersect(subs_ses1_not2,risk_subs)),
        n_ses2_not1 = length(intersect(subs_ses2_not1,risk_subs))
      )
    
    # append to task_risk_df_row to list -- this will be more efficent than appending to dataframe in a loop
    repeated_task_counts_list[[length(repeated_task_counts_list) + 1]] <- task_risk_df_row
    
  }
}

# create dataframe from list
## do.call will unpack repeated_task_counts_list and passes each dataframe individually to rbind()
repeated_task_counts <- do.call(rbind, repeated_task_counts_list)

repeated_task_counts
```


```{r task counts for non-repeated tasks, echo = FALSE  }

# unrepeated_tasks <- c("rrv_data", "spacegame_data") #uncomment when spacegame_data is returned by proc_task()
unrepeated_tasks <- c("rrv_data")

# initialize list
unrepeated_task_counts_list <- list()

# get counts for each task and risk combo, collect info in list of dataframes
for ( task in unrepeated_tasks ) {

  subs <- names(task_data[[task]])

  for (risk in c("high-risk", "low-risk")) {

    risk_subs <- participants_data[(participants_data$risk_status_maternal == risk & !is.na(participants_data$risk_status_maternal)), "participant_id"]

    # create dataframe of 1 row with counts for task/risk combo
    task_risk_df_row <-
      data.frame(
        task = task,
        risk = risk,
        n = length(intersect(subs,risk_subs))
      )
    
    # append to task_risk_df_row to list -- this will be more efficent than appending to dataframe in a loop
    unrepeated_task_counts_list[[length(unrepeated_task_counts_list) + 1]] <- task_risk_df_row
    
  }
}

# create dataframe from list 
## do.call will unpack unrepeated_task_counts_list and passes each dataframe individually to rbind()
unrepeated_task_counts <- do.call(rbind, unrepeated_task_counts_list)

unrepeated_task_counts
```

```{r task barplots, echo = FALSE  }
# unrepeated tasks
ggplot(unrepeated_task_counts, aes(x = task, y = n, fill = risk)) +
  geom_col(position = "dodge") + #geom_col makes heights of the bars to represent values in the data with stat_identity()
  labs(title = "Data collection of single-session tasks by risk group") + 
  xlab("Task") +
  theme_minimal()

# repeated tasks
repeated_task_counts_long <- repeated_task_counts %>%
  pivot_longer(cols = n_ses1_and2:n_ses2_not1, names_to = "session_cat", values_to = "n")
  
ggplot(repeated_task_counts_long, aes(x = session_cat, y = n, fill = risk)) + 
  geom_bar(stat = 'identity', position = 'stack') + facet_grid(~ task) +
  labs(title = "Data collection of repeated tasks by session and risk group")
```

