---
title: ""
author: "baf44"
date: ""
output: html_document
editor_options: 
  chunk_output_type: console
---

## Set up

```{r imports, message=FALSE, warning=FALSE}

# packages
library(dplyr)
library(tidyr)
library(ggplot2)
library(table1)

# load behavioral files generated by /ParticipantData/bids/code/beh_into_bids.R (run locally)

sst_byrun <- read.delim("~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/b-childfoodlab_Shared/Active_Studies/MarketingResilienceRO1_8242020/ParticipantData/bids/derivatives/beh_summary_databases/sst_long_by_run.tsv", na.strings = "n/a")

sst_bycond <- read.delim("~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/b-childfoodlab_Shared/Active_Studies/MarketingResilienceRO1_8242020/ParticipantData/bids/derivatives/beh_summary_databases/sst_long_by_cond.tsv", na.strings = "n/a")

participants <- read.delim("~/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/b-childfoodlab_Shared/Active_Studies/MarketingResilienceRO1_8242020/ParticipantData/bids/participants.tsv", na.strings = "n/a")

```

# Data processing

Data was processed by dataREACHr functions util_task_sst.R (called by proc_task.R) and deriv_sst.R. The following cleaning steps occurred:

1.  

2.  

3.  

Prior to computing completion and performance metrics, lets exclude data from subjects with known technical issues or protocol deviations.

```{r clean and subset data }

technical_issues = list(
  "sub-003" = "trigger interference",
  "sub-006" = "trigger interference",
  "sub-009" = "stuck button",
  "sub-013" = "stuck button",
  "sub-075" = "responses not collecting"
)

# remove subjects with known technical issues

sst_byrun_cleaned <- sst_byrun[!sst_byrun$sub %in% names(technical_issues),]
sst_bycond_cleaned <- sst_bycond[!sst_bycond$sub %in% names(technical_issues),]

# subset fmri data and remove ID 12 because their fmri data was not collected in scanner (due to child declining scan)
fmri_byrun <- sst_byrun_cleaned[sst_byrun_cleaned$type == "fMRI" & sst_byrun_cleaned$sub != "sub-012",] 
fmri_bycond <- sst_bycond_cleaned[sst_bycond_cleaned$type == "fMRI" & sst_bycond_cleaned$sub != "sub-012",] 

# subset beh data
beh_bycond <- sst_bycond_cleaned[sst_bycond_cleaned$type == "Beh",] 

```



# fMRI task completion

```{r number of runs completed and passed, warning=FALSE, message=FALSE}

# count number of children with N runs completed
run_count_by_sub <- fmri_byrun %>% group_by(sub) %>% summarise(
  n_complete = n(),
  n_pass = sum(racehorse_check==1)
) 

long_table_A <- run_count_by_sub %>% group_by(n_complete) %>% 
  summarise(
    n_subs = n(),
    metric = "completed"
  ) %>% rename('n_runs' = 'n_complete')

long_table_B <- run_count_by_sub %>% group_by(n_pass) %>% 
  summarise(
    n_subs = n(),
    metric = "passed assumption"
  ) %>% rename('n_runs' = 'n_pass')

# grouped barplot 
ggplot(rbind(long_table_A, long_table_B), aes(fill=metric, y=n_subs, x=n_runs)) + 
    geom_bar(position="dodge", stat="identity") +
    ggtitle("Stop Signal Task fMRI task status") +
    xlab("Number of runs") +
    ylab("Number of children") + 
    scale_fill_discrete(name = "Run status") +
    scale_x_continuous(breaks=c(seq(1:6))) +
    theme_bw() + 
    theme(plot.title = element_text(hjust = 0.5))

```

```{r completion and assumption check by run, warning=FALSE, message=FALSE}

# count number of children with N runs completed
count_by_run <- fmri_byrun %>% group_by(run_num) %>% summarise(
  n_complete = n(),
  n_pass = sum(racehorse_check==1)
) %>% pivot_longer(!run_num, names_to = "condition", values_to = "count")


#  barplot - complete and pass
ggplot(count_by_run, aes(fill=condition, y=count, x=as.character(run_num))) + 
    geom_bar(position="dodge", stat="identity") +
    xlab("SST Run") +
  ylab("Number of scans") + theme_bw() +
  theme(axis.text=element_text(size=24, colour = "black"), axis.title =element_text(size=24, face = "bold", colour = "black"),
        legend.text = element_text(size=24, colour = "black"),
        legend.title = element_text(size=24, colour = "black"))

# barplot - complete only
ggplot(count_by_run[count_by_run$condition == "n_complete",], aes(y=count, x=as.character(run_num))) + 
  geom_bar(position="dodge", stat="identity") + theme_bw() + ylim(0, 65) +
  xlab("SST Run") +
  ylab("Number of scans") + 
  theme(axis.text=element_text(size=24, colour = "black"), axis.title =element_text(size=24, face = "bold", colour = "black"))

```


```{r task completion based on beh, warning=FALSE, message=FALSE}

# add risk to mriqc_runs
fmri_byrun <- fmri_byrun %>% left_join(participants[c("participant_id", "risk_status_maternal")], by = join_by(sub == participant_id))


# stacked: by risk 
ggplot(fmri_byrun, aes(x = run_num, fill = risk_status_maternal)) +
  geom_bar() + theme_bw() + ylim(0, 70) +
  xlab("SST Run") +
  ylab("Number of scans") + 
  theme(axis.text=element_text(size=20, colour = "black"), 
        axis.title =element_text(size=20, face = "bold", colour = "black"),
        legend.text = element_text(size=20),
        legend.title = element_text(size=20)) +
  scale_fill_discrete(name = "Risk Status", type=c("coral","skyblue", "grey"))

```

# Performance Metrics

```{r prep metrics, warning=FALSE, message=FALSE}


sst_bycond_cleaned$prop_go_miss <- sst_bycond_cleaned$n_go_miss / sst_bycond_cleaned$n_stop_trials
  
```

## By condition (food vs. toy)

fMRI runs
```{r performance metrics by condition - fMRI runs, warning=FALSE, message=FALSE}

# subset fmri runs
fmri_bycond <- sst_bycond_cleaned[sst_bycond_cleaned$type == "fMRI" ,]

ggplot(fmri_bycond, aes(x=ssd_mean, fill=commerical_cond)) + 
   xlab("Average Stop Signal Delay") + 
  ylab("Number of children") +
  geom_histogram(alpha=0.4, position="identity") + theme_bw() + theme(axis.text=element_text(size=24, colour = "black"), axis.title =element_text(size=24, face = "bold", colour = "black"),
        legend.text = element_text(size=18, colour = "black"),
        legend.title = element_text(size=18, colour = "black")) +
  guides(fill=guide_legend(title="Commericial \nCondition"))

ggplot(fmri_bycond, aes(x=ssrt_int, fill=commerical_cond)) + 
  geom_histogram(alpha=0.4, position="identity") + theme_bw()

ggplot(fmri_bycond, aes(x = ssrt_mean, fill = commerical_cond)) +
  geom_histogram(alpha = 0.4, position = "identity") + theme_bw() +
  xlab("Stop Signal Reaction Time (mean go rt - mean ssd)") +
  ylab("Number of children") +
  geom_histogram(alpha = 0.4, position = "identity") + theme_bw() + theme(
    axis.text = element_text(size = 24, colour = "black"),
    axis.title = element_text(
      size = 24,
      face = "bold",
      colour = "black"
    ),
    legend.text = element_text(size = 18, colour = "black"),
    legend.title = element_text(size = 18, colour = "black")
  ) +
  guides(fill = guide_legend(title = "Commericial \nCondition"))


ggplot(fmri_bycond, aes(x=prop_stop_fail, fill=commerical_cond)) + 
  geom_histogram(alpha=0.4, position="identity") + theme_bw() + xlim(c(0, 1)) +
     xlab("Proportion stop failure") + 
  ylab("Number of children") +
  geom_histogram(alpha=0.4, position="identity") + theme_bw() + theme(axis.text=element_text(size=24, colour = "black"), axis.title =element_text(size=24, face = "bold", colour = "black"),
        legend.text = element_text(size=18, colour = "black"),
        legend.title = element_text(size=18, colour = "black")) +
  guides(fill=guide_legend(title="Commericial \nCondition"))


ggplot(fmri_bycond, aes(x=go_correct_rt_mean, fill=commerical_cond)) + 
  geom_histogram(alpha=0.4, position="identity") + theme_bw()

ggplot(fmri_bycond, aes(x=prop_go_miss, fill=commerical_cond)) + 
  geom_histogram(alpha=0.4, position="identity") + theme_bw() 

ggplot(fmri_bycond, aes(x=n_go_miss, fill=commerical_cond)) + 
  geom_histogram(alpha=0.4, position="identity") + theme_bw() 

ggplot(fmri_bycond, aes(x=go_error_rt_mean, fill=commerical_cond)) + 
  geom_histogram(alpha=0.4, position="identity") + theme_bw()

```


```{r table ofperformance metrics by condition - Beh runs}
# create table
table1(~ ssd_mean + ssrt_int + ssrt_mean + prop_stop_fail + go_correct_rt_mean + n_go_miss + go_error_rt_mean | commerical_cond, data=fmri_bycond)

```


Behavioral Runs
```{r performance metrics by condition - Beh runs, warning=FALSE, message=FALSE}

ggplot(beh_bycond, aes(x=ssd_mean, fill=commerical_cond)) + 
  geom_histogram(alpha=0.4, position="identity") + theme_bw()

ggplot(beh_bycond, aes(x=ssrt_int, fill=commerical_cond)) + 
  geom_histogram(alpha=0.4, position="identity") + theme_bw()

ggplot(beh_bycond, aes(x=ssrt_mean, fill=commerical_cond)) + 
  geom_histogram(alpha=0.4, position="identity") + theme_bw()

ggplot(beh_bycond, aes(x=prop_stop_fail, fill=commerical_cond)) + 
  geom_histogram(alpha=0.4, position="identity") + theme_bw() + xlim(c(0, 1))

ggplot(beh_bycond, aes(x=go_correct_rt_mean, fill=commerical_cond)) + 
  geom_histogram(alpha=0.4, position="identity") + theme_bw()

# change this to % ??
ggplot(beh_bycond, aes(x=n_go_miss, fill=commerical_cond)) + 
  geom_histogram(alpha=0.4, position="identity") + theme_bw()

ggplot(beh_bycond, aes(x=go_error_rt_mean, fill=commerical_cond)) + 
  geom_histogram(alpha=0.4, position="identity") + theme_bw()

```

```{r table ofperformance metrics by condition - Beh runs}
# create table
table1(~ ssd_mean + ssrt_int + ssrt_mean + prop_stop_fail + go_correct_rt_mean + n_go_miss + go_error_rt_mean | commerical_cond, data=beh_bycond)

```

## By run 
     
```{r performance metrics by run -- fmri}

ggplot(fmri_byrun, aes(x=go_error_rt_mean, fill=commerical_cond)) + 
  geom_histogram(alpha=0.4, position="identity") +
  theme_bw() +
  facet_grid(.~run_num)

```

